---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{odestitch}`

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/mawds/odestitch/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mawds/odestitch/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

This is a small Shiny app that plots interesting ODEs (at present only the [Lorentz System](https://en.wikipedia.org/wiki/Lorenz_system) is supported). A 2d projection of the solution can then be exported to SVG. The resulting SVG file can be imported into [Inkscape](https://inkscape.org/) where the [Inkstitch plugin](https://inkstitch.org/) can be used to output a file suitable for machine embroidery.

### Inkstitch

Having generated an svg file the following briefly explains how to convert this
to a suitable format for emboridery using Inkstitch:

Load the exported SVG file into Inkstitch
Select the resulting curve
Choose Extensions -> Ink/Stitch -> Params
Set method to "Manual stitch" - each timestep will then be a single stitch
(You may wish to set maximum stitch length if some time-steps result in large jumps)
You can then save the file in the appropriate format for your machine.

#### Troubleshooting

If you're running Linux, and find Inkstitch's dialogue boxes don't appear, 
restart Inkscape with:

```{bash, eval = FALSE}
export GDK_BACKEND=x11 && inkscape
```

[This is because Inkstitch doesn't work properly with Wayland](https://inkstitch.org/docs/install-linux/#some-inkstitch-dialogs-disappear-after-a-few-seconds-or-dont-show-up-at-all)



## Installation

You can install the package by cloning the repo and, from the project directory running:

```{r, eval = FALSE}
devtools::install()
```

## Run

You can launch the application locally by running:

```{r, eval = FALSE}
odestitch::run_app()
```

## Deployment

To deploy to shinyapps.io

```{r, eval = FALSE}
options(rsconnect.packrat = TRUE)
rsconnect::deployApp()
```

(see https://github.com/ThinkR-open/golem/issues/1070) for why we need to use
packrat



## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("odestitch")
```

```{r, error = TRUE}
covr::package_coverage()
```
